%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% setup.tex
% Main tex file for setup and content collocation
% For the use of University of Amsterdam
% Information Systems and Data Science students
% Adapted by Riccardo Fiorista (riccardo.fiorista@proton.me)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Options:
% Choose one of:
%% `is` - Information Systems
%% `ds` - Data Science 
% Add (separated by `,`):
%% `nolinenumbering` - If you want to remove line numbering on submission
%% `draftmargins` - If you would like to give your reviewer more space for comments
%% `nofrontpicture` - If you do not wish to have a graphic on your front-page
%% `nofirstcompanypicture` - If you do not wish to have a graphic on your front-page
%% `nosecondcompanypicture` - If you do not wish to have a graphic on your front-page
\documentclass[ds, nofrontpicture, nolinenumbering, nosecondcompanypicture, nofirstcompanypicture]{mscthesis}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% DOCUMENT METADATA
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Thesis related entries
\title{AccessiPub: Automating EPUB Accessibility}
\subtitle{Introducing a new method to increase EPUB accessibility automatically}

% Date on which your thesis is submitted
\date{30.06.2024}

% 4-5 keywords should do the trick. They should ideally be phrases of 2-4 words or single words.
\keywords{EPUB, accessibility automation, WCAG, HTML refactoring, tool development}

% Author data
\authorname{Sascha Kolthof}
\authorid{12851981}
\authoremail{sascha.kolthof@student.uva.nl}

% Supervisors
\uvasupervisorname{Yixian Shen}
\uvasupervisoraffiliation{UvA Supervisor}
\uvasupervisoremail{y.shen@uva.nl}

% % Comment if you do not have an external supervisor
% \externalsupervisorname{External Supervisor} \externalsupervisoraffiliation{External Supervisor}
% \externalsupervisoremail{supervisor@company.nl}

% % Uncomment and fill paths if you want to add custom images
% %% Figure size suggestions (in general it's best to render them from SVGs):
% %% 3000x3000 @ 240dpi for all three
% \titlepicturepath{}
% \firstcompanypicturepath{}
% \secondcompanypicture{path}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% CONTENT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\pagestyle{plain}

\maketitlepage
\fixemptypage
\setcounter{page}{1}

\begin{abstract}
\thispagestyle{plain}
The EPUB file format is an open-to-use file format with many accessibility perks. For visually impaired people, EPUBs can provide great benefits. EPUBs work well with assistive technologies and can adapt dynamically to alterations such as font size and style changes. 
Unfortunately, many EPUBs do not adhere to the most recent guidelines put in place by the EPUB Accessibility standard. Current academia has not yet explored the possibility of automating the process of making EPUBs more accessible. 
This thesis therefore formulates a new methodology, called AccessiPub, to enhance EPUB accessibility automatically. The Ace checker is leveraged, along with new methods to locate accessibility errors inside the EPUB. Then, drawing from existing literature, HTML refactoring is adapted to fit the EPUB file type. Lastly, a novel way to disassemble and reassemble EPUBs is created using EbookLib and ZipFile. 
The developed methodology was able to reduce the amount of target errors by 97.8\%. Compared to similar research, this result is very promising and lights up the path ahead for further research into automatic EPUB accessibility enhancement.
\end{abstract}

\maketitle

% UNCOMMENT THIS LINE BEFORE EXPORTING FINAL (?)
\section*{GitHub Repository}
\small
\url{https://github.com/SaschaUvA/Accessible-ePubs-Thesis-Sascha-Kolthof}
\normalsize

% Sections; Try to stick to this setup but you can comment each section
\input{sections/2-thesis/1-introduction.tex}
\input{sections/2-thesis/2-related-work.tex}
\input{sections/2-thesis/3-methodology.tex}
\input{sections/2-thesis/4-results.tex}
\input{sections/2-thesis/5-discussion.tex}
\input{sections/2-thesis/6-conclusion.tex}

\bibliographystyle{ACM-Reference-Format}
\bibliography{bibliographies/references}

\newpage
\input{sections/2-thesis/7-appendix.tex}

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%